Motor Vehicle Collisions Reduced Across Toronto During and After the Beginning of the COVID-19 Pandemic

### 2024-01-23 outputs/paper/paper.qmd
Updated wording in introduction of paper

By understanding collision trends across Toronto and over the years, it can help improved safety plans for strategies like Vision Zero for instance for pedestrians in specific areas of Toronto.

>>>>

By understanding collision trends across Toronto and over the years, it can assist with how current safety plans like Vision Zero can improve and assist with being more strategic such as safety plans in specific locations of Toronto.
